---
output:
  md_document:
    variant: markdown_github
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# otsad

*Online Time Series Anomaly Detectors*

This package provides anomaly detectors in the context of online time series and their evaluation with the Numenta score.

## Installation


### Dependencies

CAD-OSE algorithm is implemented in Python. It uses [bencode](https://pypi.org/project/bencode-python3/) library in the hashing step. This dependency can be installed with the Python package manager *pip*.

```sh
$ sudo pip install bencode-python3
```

### otsad package

You can install the released version of otsad from [CRAN](https://CRAN.R-project.org) with:

```{r installation, eval=FALSE}
# Get the released version from CRAN
install.packages("otsad")

# Get the latest development version from GitHub
devtools::install_github("alaineiturria/otsad")
```

## Most useful functions

### Detectors

* **PEWMA**
    + Offline: CpPewma
    + Online: IpPewma
* **SD-EWMA**
    + Offline: CpSdEwma
    + Online: IpSdEwma
* **TSSD-EWMA**
    + Offline: CpTsSdEwma
    + Online: IpTsSdEwma
* **KNN-ICAD**
    + Offline: CpKnnCad(ncm.type = "ICAD")
    + Online: IpKnnCad(ncm.type = "ICAD")
* **KNN-LDCD**
    + Offline CpKnnCad(ncm.type = "LDCD")
    + Online: IpKnnCad(ncm.type = "LDCD")
* **CAD-OSE**
    + Offline and Online: ContextualAnomalyDetector
    
### NAB score

* Get score: GetDetectorScore
* Normalize score: NormalizeScore + GetNullAndPerfectScores

### False Positve Reduction

* Offline and Online: ReduceAnomalies

### Static or interactive visualizations 

* Offline: PlotDetections

<div style="background-color: #cceeff; padding: 10px;">

***NOTE:*** *As usual in R, the documentation pages for each function can be loaded from the command line with the commands ? or help:*

``` r
?CpSdEwma
help(CpSdEwma)
```
</div>

## Example

This is a basic example of the use of otsad package:

```{r example}
library(otsad)

## basic example code

# Generate data
set.seed(100)
n <- 500
x <- sample(1:100, n, replace = TRUE)
x[70:90] <- sample(110:115, 21, replace = TRUE) # distributional shift
x[25] <- 200 # abrupt transient anomaly
x[320] <- 170 # abrupt transient anomaly
df <- data.frame(timestamp = 1:n, value = x)

# Apply classic processing SD-EWMA detector
result <- CpSdEwma(data = df$value, n.train = 5, threshold = 0.01, l = 3)
```



```{r plot.Anomaly}
res <- cbind(df, result)
PlotDetections(res, title = "SD-EWMA ANOMALY DETECTOR", return.ggplot = TRUE)
```

See plotly [interactive graph](https://alaineiturria.github.io/otsad/)

For more details, see otsad documentation and vignettes.


